Tor's Usability for Censorship Circumvention

### 2015-12-10 paper/circumvention-experiment.tex
visualizing markov complete

One exciting analysis we will perform is to build a Markov model of the UI flow chart (like the one seen in Figure \ref{fig:interface}). We believe that this will be helpful in communicating participant behavior in aggregate since it will show the change in the UI flow structure, as well as how participants decisions have changed (e.g., in the old interface, a participant in a censorship environment which does not block Tor has a 0.4 chance of choosing ``connect,'' whereas in the new interface, the probability is 0.6). We have other visualizations in mind to display all participants' window traversal at a glance (Figure \ref{fig:bar} shows an illustration), as well as other analyses.\\

>>>>

One exciting analysis we will perform is to build a Markov model of the UI flow chart (Figure \ref{fig:markov} shows a simplified illustration). We believe that this will be helpful in communicating participant behavior in aggregate since it will show the change in the UI flow structure, as well as how participants decisions have changed (e.g., in the old interface, a participant in a censorship environment which does not block Tor has a 0.4 chance of choosing ``connect,'' whereas in the new interface, the probability is 0.6). We have other visualizations in mind to display all participants' window traversal at a glance (Figure \ref{fig:bar} shows a simplified illustration), as well as other analyses.\\

\begin{figure}[t]
\label{fig:markov}
  \centering
    \includegraphics[width=0.5\textwidth]{markov.png}
    \caption{An illustration on a planned analysis using the quantitative survey data. This illustration shows two possible user interfaces and uses a Markov model to reflect the aggregate user behavior. We believe that this will be an concrete way to predict user behaviors, which is valuable feedback for if the interface is guiding users in a desired UI path.}
\end{figure}
